---
title: "Revision report"
author: 'M'
date: "2025-03-13"
output:
  html_document:
    highlight: tango
    theme: readable
    toc: yes
    toc_float: 
      collapsed: false
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(dplyr)
library(ggplot2)
library(reshape2)
```
```{r echo=F}
ci_tidy <- function(CIs){
  cbind(paste0(format(CIs[, 1] * 100, nsmall = 1), " (", format(CIs[, 4], nsmall = 1), ")"),
        paste0(format(CIs[, 2] * 100, nsmall = 1), " (", format(CIs[, 5], nsmall = 1), ")"),
        paste0(format(CIs[, 3] * 100, nsmall = 1), " (", format(CIs[, 6], nsmall = 1), ")")) -> ci
  colnames(ci) = c("t=0.4", "t=0.6", "t=0.8")
  return(ci)
}
```




# Simulations: Table 1, 2, 4 and Figure 2.

## n = 60
```{r}
n = 60
load(file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/MISES.rdata"))
write.csv(MISEs, file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/MISEs.csv"))
MISEs
load(file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/CIs.rdata"))
write.csv(CIs, file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/CIs.csv"))
CIs
```


## n = 100
```{r}
n = 100
load(file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/MISES.rdata"))
write.csv(MISEs, file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/MISEs.csv"))
MISEs
load(file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/CIs.rdata"))
write.csv(CIs, file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/CIs.csv"))
CIs
```

## n = 200
```{r}
n = 200
load(file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/MISES.rdata"))
write.csv(MISEs, file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/MISEs.csv"))
MISEs
load(file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/CIs.rdata"))
write.csv(CIs, file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/CIs.csv"))
CIs
```

## n = 500
```{r}
n = 500
load(file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/MISES.rdata"))
write.csv(MISEs, file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/MISEs.csv"))
MISEs
load(file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/CIs.rdata"))
write.csv(CIs, file = paste0("simuresult_Tab1-4_Fig2/re_n=", n, "/CIs.csv"))
CIs
```

# Simulations: Table 3: Different initial values

## Ini = 0; True
```{r}
ini = 0
load(file = paste0("simu_ini_change/re_ini=", ini, "/MISES.rdata"))
write.csv(MISEs, file = paste0("simu_ini_change/re_ini=", ini, "/MISEs.csv"))
MISEs
```
```{r}
load(file = paste0("simu_ini_change/re_ini=", ini, "/CIs.rdata"))
write.csv(CIs, file = paste0("simu_ini_change/re_ini=", ini, "/CIs.csv"))
CIs
```
```{r}
Runningtime = read.csv(file = paste0("simu_ini_change/re_ini=", ini, "/time.csv"))
Runningtime
```

## Ini = -1
```{r}
ini = -1
load(file = paste0("simu_ini_change/re_ini=", ini, "/MISES.rdata"))
write.csv(MISEs, file = paste0("simu_ini_change/re_ini=", ini, "/MISEs.csv"))
MISEs
```
```{r}
load(file = paste0("simu_ini_change/re_ini=", ini, "/CIs.rdata"))
write.csv(CIs, file = paste0("simu_ini_change/re_ini=", ini, "/CIs.csv"))
CIs
```
```{r}
Runningtime = read.csv(file = paste0("simu_ini_change/re_ini=", ini, "/time.csv"))
Runningtime
```

## Ini = 2
```{r}
ini = 2
load(file = paste0("simu_ini_change/re_ini=", ini, "/MISES.rdata"))
write.csv(MISEs, file = paste0("simu_ini_change/re_ini=", ini, "/MISEs.csv"))
MISEs
```
```{r}
load(file = paste0("simu_ini_change/re_ini=", ini, "/CIs.rdata"))
write.csv(CIs, file = paste0("simu_ini_change/re_ini=", ini, "/CIs.csv"))
CIs
```
```{r}
Runningtime = read.csv(file = paste0("simu_ini_change/re_ini=", ini, "/time.csv"))
Runningtime
```

## Ini = 5
```{r}
ini = 5
load(file = paste0("simu_ini_change/re_ini=", ini, "/MISES.rdata"))
write.csv(MISEs, file = paste0("simu_ini_change/re_ini=", ini, "/MISEs.csv"))
MISEs
```
```{r}
load(file = paste0("simu_ini_change/re_ini=", ini, "/CIs.rdata"))
write.csv(CIs, file = paste0("simu_ini_change/re_ini=", ini, "/CIs.csv"))
CIs
```
```{r}
Runningtime = read.csv(file = paste0("simu_ini_change/re_ini=", ini, "/time.csv"))
Runningtime
```


# Simulations: Figure 3: Bias of K'th method
```{r echo=FALSE}
knitr::include_graphics(paste0("simu_fig3/b=0.pdf"))
knitr::include_graphics(paste0("simu_fig3/b=0.33.pdf"))
knitr::include_graphics(paste0("simu_fig3/b=0.5.pdf"))
knitr::include_graphics(paste0("simu_fig3/b=1.pdf"))
```

# Simulations: Z dependent

## rho = 0.2
```{r}
rho = 0.2
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/alpha1.pdf"))
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/beta1.pdf"))
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/gamma1.pdf"))
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/gamma2.pdf"))
```

## rho = 0.4
```{r}
rho = 0.4
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/alpha1.pdf"))
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/beta1.pdf"))
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/gamma1.pdf"))
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/gamma2.pdf"))
```

## rho = 0.6
```{r}
rho = 0.6
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/alpha1.pdf"))
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/beta1.pdf"))
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/gamma1.pdf"))
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/gamma2.pdf"))
```

## rho = 0.8
```{r}
rho = 0.8
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/alpha1.pdf"))
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/beta1.pdf"))
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/gamma1.pdf"))
knitr::include_graphics(paste0("simu_z_dependent/re_n=100rho=", rho, "/gamma2.pdf"))
```


# Simulation: Goodness of fit Case 1

## Our's method ( effect)
```{r echo=F}
load("goodness_of_fit/es_Ni_case_1.rdata")
load("goodness_of_fit/es_Nj_case_1.rdata")
iseq <- c(1:100)
re_i <- c()
for(i in iseq){
  re <- cbind(t(es_Ni_list[[i]]), i)
  colnames(re) <- c("Number of events of senders", "Esimtated cumulative intensity", "Sender")
  re_i <- rbind(re_i, re)
}
re_i %>% as.data.frame() -> re_i
# re_i$Sender %>% as.factor() -> re_i$Sender

 
re_j <- c()
for(j in iseq){
  re <- cbind(t(es_Nj_list[[j]]), j)
  colnames(re) <- c("Number of events of receivers", "Esimtated cumulative intensity", "Receiver")
  re_j <- rbind(re_j, re)
}
re_j %>% as.data.frame() -> re_j
# re_j$Receiver %>% as.factor() -> re_j$Receiver

```

```{r echo=F}
ggplot(re_i, aes(x = `Number of events of senders`, y = `Esimtated cumulative intensity`, color = `Sender`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "Our methods: sender",
       x = "Number of events of senders",
       y = "Estimated cumulative intensity") +
  theme_minimal()
```
```{r echo=F}
ggplot(re_j, aes(x = `Number of events of receivers`, y = `Esimtated cumulative intensity`, color = `Receiver`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "Our methods: receiver",
       x = "Number of events of receivers",
       y = "Estimated cumulative intensity") +
  theme_minimal()
```



## K's method (homo effect)

```{r echo=F}
load("goodness_of_fit/homo_es_Ni_case_1.rdata")
load("goodness_of_fit/homo_es_Nj_case_1.rdata")
re_i <- c()
for(i in iseq){
  re <- cbind(t(es_Ni_homo_list[[i]]), i)
  colnames(re) <- c("Number of events of senders", "Esimtated cumulative intensity", "Sender")
  re_i <- rbind(re_i, re)
}
re_i %>% as.data.frame() -> re_i
# re_i$Sender %>% as.factor() -> re_i$Sender

re_j <- c()
for(j in iseq){
  re <- cbind(t(es_Nj_homo_list[[j]]), j)
  colnames(re) <- c("Number of events of receivers", "Esimtated cumulative intensity", "Receiver")
  re_j <- rbind(re_j, re)
}
re_j %>% as.data.frame() -> re_j
# re_j$Receiver %>% as.factor() -> re_j$Receiver

```

```{r echo=F}
ggplot(re_i, aes(x = `Number of events of senders`, y = `Esimtated cumulative intensity`, color = `Sender`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "K's methods: sender",
       x = "Number of events of senders",
       y = "Estimated cumulative intensity") +
  theme_minimal()
```
```{r echo=F}
ggplot(re_j, aes(x = `Number of events of receivers`, y = `Esimtated cumulative intensity`, color = `Receiver`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "K's methods: receiver",
       x = "Number of events of receivers",
       y = "Estimated cumulative intensity") +
  theme_minimal() 
```


# Simulation: Goodness of fit Case 2

## Our's method ( effect)
```{r echo=F}
load("goodness_of_fit/es_Ni_case_2.rdata")
load("goodness_of_fit/es_Nj_case_2.rdata")
re_i <- c()
for(i in iseq){
  re <- cbind(t(es_Ni_list[[i]]), i)
  colnames(re) <- c("Number of events of senders", "Esimtated cumulative intensity", "Sender")
  re_i <- rbind(re_i, re)
}
re_i %>% as.data.frame() -> re_i
# re_i$Sender %>% as.factor() -> re_i$Sender

re_j <- c()
for(j in iseq){
  re <- cbind(t(es_Nj_list[[j]]), j)
  colnames(re) <- c("Number of events of receivers", "Esimtated cumulative intensity", "Receiver")
  re_j <- rbind(re_j, re)
}
re_j %>% as.data.frame() -> re_j
# re_j$Receiver %>% as.factor() -> re_j$Receiver

```

```{r echo=F}
ggplot(re_i, aes(x = `Number of events of senders`, y = `Esimtated cumulative intensity`, color = `Sender`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "Our methods: sender",
       x = "Number of events of senders",
       y = "Estimated cumulative intensity") +
  theme_minimal()
```
```{r echo=F}
ggplot(re_j, aes(x = `Number of events of receivers`, y = `Esimtated cumulative intensity`, color = `Receiver`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "Our methods: receiver",
       x = "Number of events of receivers",
       y = "Estimated cumulative intensity") +
  theme_minimal()
```



## K's method (homo effect)

```{r echo=F}
load("goodness_of_fit/homo_es_Ni_case_2.rdata")
load("goodness_of_fit/homo_es_Nj_case_2.rdata")
re_i <- c()
for(i in iseq){
  re <- cbind(t(es_Ni_homo_list[[i]]), i)
  colnames(re) <- c("Number of events of senders", "Esimtated cumulative intensity", "Sender")
  re_i <- rbind(re_i, re)
}
re_i %>% as.data.frame() -> re_i
# re_i$Sender %>% as.factor() -> re_i$Sender

re_j <- c()
for(j in iseq){
  re <- cbind(t(es_Nj_homo_list[[j]]), j)
  colnames(re) <- c("Number of events of receivers", "Esimtated cumulative intensity", "Receiver")
  re_j <- rbind(re_j, re)
}
re_j %>% as.data.frame() -> re_j
# re_j$Receiver %>% as.factor() -> re_j$Receiver

```

```{r echo=F}
ggplot(re_i, aes(x = `Number of events of senders`, y = `Esimtated cumulative intensity`, color = `Sender`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "K's methods: sender",
       x = "Number of events of senders",
       y = "Estimated cumulative intensity") +
  theme_minimal()
```
```{r echo=F}
ggplot(re_j, aes(x = `Number of events of receivers`, y = `Esimtated cumulative intensity`, color = `Receiver`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "K's methods: receiver",
       x = "Number of events of receivers",
       y = "Estimated cumulative intensity") +
  theme_minimal() 
```







# Simulation: Goodness of fit Case 3

## Our's method ( effect)
```{r echo=F}
load("goodness_of_fit/es_Ni_case_3.rdata")
load("goodness_of_fit/es_Nj_case_3.rdata")
re_i <- c()
for(i in iseq){
  re <- cbind(t(es_Ni_list[[i]]), i)
  colnames(re) <- c("Number of events of senders", "Esimtated cumulative intensity", "Sender")
  re_i <- rbind(re_i, re)
}
re_i %>% as.data.frame() -> re_i
# re_i$Sender %>% as.factor() -> re_i$Sender

re_j <- c()
for(j in iseq){
  re <- cbind(t(es_Nj_list[[j]]), j)
  colnames(re) <- c("Number of events of receivers", "Esimtated cumulative intensity", "Receiver")
  re_j <- rbind(re_j, re)
}
re_j %>% as.data.frame() -> re_j
# re_j$Receiver %>% as.factor() -> re_j$Receiver

```

```{r echo=F}
ggplot(re_i, aes(x = `Number of events of senders`, y = `Esimtated cumulative intensity`, color = `Sender`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "Our methods: sender",
       x = "Number of events of senders",
       y = "Estimated cumulative intensity") +
  theme_minimal()
```
```{r echo=F}
ggplot(re_j, aes(x = `Number of events of receivers`, y = `Esimtated cumulative intensity`, color = `Receiver`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "Our methods: receiver",
       x = "Number of events of receivers",
       y = "Estimated cumulative intensity") +
  theme_minimal()
```



## K's method (homo effect)

```{r echo=F}
load("goodness_of_fit/homo_es_Ni_case_3.rdata")
load("goodness_of_fit/homo_es_Nj_case_3.rdata")
re_i <- c()
for(i in iseq){
  re <- cbind(t(es_Ni_homo_list[[i]]), i)
  colnames(re) <- c("Number of events of senders", "Esimtated cumulative intensity", "Sender")
  re_i <- rbind(re_i, re)
}
re_i %>% as.data.frame() -> re_i
# re_i$Sender %>% as.factor() -> re_i$Sender

re_j <- c()
for(j in iseq){
  re <- cbind(t(es_Nj_homo_list[[j]]), j)
  colnames(re) <- c("Number of events of receivers", "Esimtated cumulative intensity", "Receiver")
  re_j <- rbind(re_j, re)
}
re_j %>% as.data.frame() -> re_j
# re_j$Receiver %>% as.factor() -> re_j$Receiver

```

```{r echo=F}
ggplot(re_i, aes(x = `Number of events of senders`, y = `Esimtated cumulative intensity`, color = `Sender`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "K's methods: sender",
       x = "Number of events of senders",
       y = "Estimated cumulative intensity") +
  theme_minimal()
```
```{r echo=F}
ggplot(re_j, aes(x = `Number of events of receivers`, y = `Esimtated cumulative intensity`, color = `Receiver`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "K's methods: receiver",
       x = "Number of events of receivers",
       y = "Estimated cumulative intensity") +
  theme_minimal() 
```








# Simulations: Cross Validation.

```{r echo=F}
# 创建示例矩阵数据
read.csv("simu_CV/n=100.csv", header = T) -> aa
rownames(aa) <- aa[, 1]
aa[, -1] -> aa
aa %>% as.matrix() -> data_matrix
# 转换为 data.frame
data_long <- melt(data_matrix, varnames = c("h1", "h2"), value.name = "value")

# 提取 h1 的数值部分作为横坐标
data_long$h1_numeric <- as.numeric(gsub("h1=", "", data_long$h1))
data_long$`h2 values` <- as.factor(gsub("h2.", "", data_long$h2))
# 绘制折线图
ggplot(data_long, aes(x = h1_numeric, y = value, group = `h2 values`, color = `h2 values`)) +
  geom_line() +
  geom_point() +
  labs(title = paste0("PE with different bendwidth value, n = 100"),
       x = "h1 Values",
       y = "PE Values") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) -> p1
p1
```
```{r eval = F, echo=F}
pdf(file = "simu_CV/n=100.pdf")
p1
dev.off()
```


# MIT Analysis

## Gamma estimation
```{r echo=FALSE}
knitr::include_graphics(paste0("mit_plots/gamma1.pdf"))
knitr::include_graphics(paste0("mit_plots/gamma2.pdf"))
knitr::include_graphics(paste0("mit_plots/gamma3.pdf"))
knitr::include_graphics(paste0("mit_plots/gamma4.pdf"))
```

## Gof: Our's method ( effect)
```{r echo=F}
load("goodness_of_fit_mit2/es_Ni.rdata")
load("goodness_of_fit_mit2/es_Nj.rdata")
re_i <- c()
for(i in c(1:63)){
  re <- cbind(t(es_Ni_list[[i]]), i)
  colnames(re) <- c("Number of events of senders", "Esimtated cumulative intensity", "Sender")
  re_i <- rbind(re_i, re)
}
re_i %>% as.data.frame() -> re_i
# re_i$Sender %>% as.factor() -> re_i$Sender

re_j <- c()
for(j in c(23:63)){
  re <- cbind(t(es_Nj_list[[j]]), j)
  colnames(re) <- c("Number of events of receivers", "Esimtated cumulative intensity", "Receiver")
  re_j <- rbind(re_j, re)
}
re_j %>% as.data.frame() -> re_j
# re_j$Receiver %>% as.factor() -> re_j$Receiver

```

```{r echo=F}
ggplot(re_i, aes(x = `Number of events of senders`, y = `Esimtated cumulative intensity`, color = `Sender`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "Our methods: sender",
       x = "Number of events of senders",
       y = "Estimated cumulative intensity") +
  theme_minimal() -> p1
p1
```


```{r echo=F, eval=F}
pdf(file = "goodness_of_fit_mit2/Our_sender.pdf")
plot(p1)
dev.off()
```
```{r echo=F}
ggplot(re_j, aes(x = `Number of events of receivers`, y = `Esimtated cumulative intensity`, color = `Receiver`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "Our methods: receiver",
       x = "Number of events of receivers",
       y = "Estimated cumulative intensity") +
  theme_minimal() -> p2
p2
```

```{r echo=F, eval=F}
pdf(file = "goodness_of_fit_mit2/Our_receiver.pdf")
plot(p2)
dev.off()
```


## Gof: K's method (homo effect)

```{r echo=F}
load("goodness_of_fit_mit2/homo_es_Ni.rdata")
load("goodness_of_fit_mit2/homo_es_Nj.rdata")
re_i <- c()
for(i in c(1:63)){
  re <- cbind(t(es_Ni_homo_list[[i]]), i)
  colnames(re) <- c("Number of events of senders", "Esimtated cumulative intensity", "Sender")
  re_i <- rbind(re_i, re)
}
re_i %>% as.data.frame() -> re_i
# re_i$Sender %>% as.factor() -> re_i$Sender

re_j <- c()
for(j in c(23:63)){
  re <- cbind(t(es_Nj_homo_list[[j]]), j)
  colnames(re) <- c("Number of events of receivers", "Esimtated cumulative intensity", "Receiver")
  re_j <- rbind(re_j, re)
}
re_j %>% as.data.frame() -> re_j
# re_j$Receiver %>% as.factor() -> re_j$Receiver

```

```{r echo=F}
ggplot(re_i, aes(x = `Number of events of senders`, y = `Esimtated cumulative intensity`, color = `Sender`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "K's methods: sender",
       x = "Number of events of senders",
       y = "Estimated cumulative intensity") + 
    ylim(c(0, 10000))+
  xlim(c(0, 10000))+
  theme_minimal() -> p1
p1
```
```{r echo=F, eval=F}
pdf(file = "goodness_of_fit_mit2/Homo_sender.pdf")
plot(p1)
dev.off()
```

```{r echo=F}
ggplot(re_j, aes(x = `Number of events of receivers`, y = `Esimtated cumulative intensity`, color = `Receiver`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "K's methods: receiver",
       x = "Number of events of receivers",
       y = "Estimated cumulative intensity") +
    ylim(c(0, 10000))+
  xlim(c(0, 10000))+
  theme_minimal() -> p2
p2
```
```{r echo=F, eval=F}
pdf(file = "goodness_of_fit_mit2/Homo_receiver.pdf")
plot(p2)
dev.off()
```





# Bike Analysis

## Alpha Beta estimation
```{r echo=F}
load(file = "bikedata/xkk0.0437599061077816_1.rdata")
load(file = "bikedata/xkkCI0.0437599061077816_1.rdata")
load(file = "bikedata/xkkHomo0.0437599061077816_1.rdata")
ftrans = function(t) {
  return(as.Date("20180501", format = "%Y%m%d") + (as.Date("20180531", format = "%Y%m%d") - as.Date("20180501", format = "%Y%m%d")) * t)
}
n = 417
ave1 = colSums(xkk[1:n,])/n
ave2 = colSums(xkk[(n+1):(2*n-1),])/(n-1)
for(pk in c(1, 101, 201, 301, 401)){
# ALPHA
p1 = data.frame(t1 = seq(0.1,0.9,0.01) %>% ftrans(), 
                t2 = seq(0.1, 0.9, 0.01), 
                y = xkk[pk,] - ave1,
                yl = xkk[pk,] - ave1 - 1.96*xkkCI[pk,],
                yu = xkk[pk,] - ave1 + 1.96*xkkCI[pk,])

# BETA
p2 = data.frame(t1 = seq(0.1,0.9,0.01) %>% ftrans(), 
                t2 = seq(0.1, 0.9, 0.01),  
                y = xkk[pk+n,] - ave2,
                yl = xkk[pk+n,] - ave2 - 1.96*xkkCI[pk,],
                yu = xkk[pk+n,] - ave2 + 1.96*xkkCI[pk,])

# 1a
ggplot(p1, aes(x = t2, y = y)) +
  geom_line(color = "red", size = 0.75) +
  geom_ribbon(aes(ymin = yl, ymax = yu), alpha = 0, color = "red", linetype = "dashed", size = 0.75) +  # 添加fill颜色映射
  scale_x_continuous(
    breaks = seq(0.1, 0.9, by = 0.2),  # 调整间隔为每0.2显示一个标签
    labels = function(t) {
      format(ftrans(t), "%b %d")       # 将数值转换为日期格式
    }
  ) +
  xlab(expression(italic("t"))) +
  ylab(expression(widehat(italic(alpha))[i]^"'"~(t))) +
  ylim(-5, 5)+
  theme(panel.background = element_rect(fill = "white")) + 
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1)) -> f1
plot(f1)

# 1b
ggplot(p2, aes(x = t2, y = y)) +
  geom_line(color = "red", size = 0.75) +
  geom_ribbon(aes(ymin = yl, ymax = yu), alpha = 0, color = "red", linetype = "dashed", size = 0.75) +# 添加fill颜色映射
  scale_x_continuous(
    breaks = seq(0.1, 0.9, by = 0.2),  # 调整间隔为每0.2显示一个标签
    labels = function(t) {
      format(ftrans(t), "%b %d")       # 将数值转换为日期格式
    }
  ) +
  xlab(expression(italic("t"))) +
  ylab(expression(widehat(italic(beta))[i]^"'"~(t))) +
  ylim(-5, 5)+
  theme(panel.background = element_rect(fill = "white")) + 
  theme(panel.border = element_rect(color = "black", fill = NA, size = 1)) -> f2
plot(f2)
}
```

## Gamma estimation
```{r, echo=F}
load(file = "bikedata/xkk0.0437599061077816_1.rdata")
load(file = "bikedata/xkkCI0.0437599061077816_1.rdata")
load(file = "bikedata/xkkHomo0.0437599061077816_1.rdata")
n = 417
pp = 1
ftrans = function(t) {
  return(as.Date("20180501", format = "%Y%m%d") + (as.Date("20180531", format = "%Y%m%d") - as.Date("20180501", format = "%Y%m%d")) * t)
}
p1 = data.frame(t1 = seq(0.1,0.9,0.01) %>% ftrans(), 
                t2 = seq(0.1,0.9,0.01),
                y = c(xkk[2*n - 1 + pp,], xkkHomo[pp,]),
                yl = c(xkk[2*n - 1 + pp,] - 1.96*xkkCI[2*n - 1 + pp,], xkkHomo[pp,]),
                yu = c(xkk[2*n - 1 + pp,] + 1.96*xkkCI[2*n - 1 + pp,], xkkHomo[pp,]),
                het = c(rep("y", 81), rep("n", 81)))

# sf
ggplot(p1, aes(x = t2, y = y, group = het, colour = het, fill = het)) +
  geom_line() +
  geom_ribbon(aes(ymin = yl, ymax = yu), alpha = 0, linetype = "dashed", size = 0.7) + 
  scale_color_manual(values = c("#619CFF", "red")) +
  scale_fill_manual(values = c("#619CFF", "red")) +  # 添加fill颜色映射
  scale_x_continuous(
    breaks = seq(0.1, 0.9, by = 0.2),  # 调整间隔为每0.2显示一个标签
    labels = function(t) {
      format(ftrans(t), "%b %d")       # 将数值转换为日期格式
    }
  ) +
  xlab(expression(italic("t"))) +
  ylab(expression(widehat(italic(gamma))[1](t))) +
  theme(
    panel.background = element_rect(fill = "white"),
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    legend.position = "none"
  )
```


```{r, echo=F}
pp = 2
p1 = data.frame(t1 = seq(0.1,0.9,0.01) %>% ftrans(), 
                t2 = seq(0.1,0.9,0.01),
                y = c(xkk[2*n - 1 + pp,], xkkHomo[pp,]),
                yl = c(xkk[2*n - 1 + pp,] - 1.96*xkkCI[2*n - 1 + pp,], xkkHomo[pp,]),
                yu = c(xkk[2*n - 1 + pp,] + 1.96*xkkCI[2*n - 1 + pp,], xkkHomo[pp,]),
                het = c(rep("y", 81), rep("n", 81)))

# sf
ggplot(p1, aes(x = t2, y = y, group = het, colour = het, fill = het)) +
  geom_line() +
  geom_ribbon(aes(ymin = yl, ymax = yu), alpha = 0, linetype = "dashed", size = 0.7) + 
  scale_color_manual(values = c("#619CFF", "red")) +
  scale_fill_manual(values = c("#619CFF", "red")) +  # 添加fill颜色映射
  scale_x_continuous(
    breaks = seq(0.1, 0.9, by = 0.2),  # 调整间隔为每0.2显示一个标签
    labels = function(t) {
      format(ftrans(t), "%b %d")       # 将数值转换为日期格式
    }
  ) +
  xlab(expression(italic("t"))) +
  ylab(expression(widehat(italic(gamma))[2](t))) +
  theme(
    panel.background = element_rect(fill = "white"),
    panel.border = element_rect(color = "black", fill = NA, size = 1),
    legend.position = "none"
  )
```


## Gof: Our's method ( effect)
```{r echo=F}
load("goodness_of_fit_bike/es_Ni.rdata")
load("goodness_of_fit_bike/es_Nj.rdata")
re_i <- c()
for(i in iseq){
  re <- cbind(t(es_Ni_list[[i]]), i)
  colnames(re) <- c("Number of events of senders", "Esimtated cumulative intensity", "Sender")
  re_i <- rbind(re_i, re)
}
re_i %>% as.data.frame() -> re_i
# re_i$Sender %>% as.factor() -> re_i$Sender

re_j <- c()
for(j in iseq){
  re <- cbind(t(es_Nj_list[[j]]), j)
  colnames(re) <- c("Number of events of receivers", "Esimtated cumulative intensity", "Receiver")
  re_j <- rbind(re_j, re)
}
re_j %>% as.data.frame() -> re_j
# re_j$Receiver %>% as.factor() -> re_j$Receiver

```

```{r echo=F}
ggplot(re_i, aes(x = `Number of events of senders`, y = `Esimtated cumulative intensity`, color = `Sender`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "Our methods: sender",
       x = "Number of events of senders",
       y = "Estimated cumulative intensity") +
  theme_minimal() -> p1
p1
```
```{r echo=F, eval=F}
pdf(file = "goodness_of_fit_bike/Our_sender.pdf")
plot(p1)
dev.off()
```

```{r echo=F}
ggplot(re_j, aes(x = `Number of events of receivers`, y = `Esimtated cumulative intensity`, color = `Receiver`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "Our methods: receiver",
       x = "Number of events of receivers",
       y = "Estimated cumulative intensity") +
  theme_minimal() -> p2
p2
```

```{r echo=F, eval=F}
pdf(file = "goodness_of_fit_bike/Our_receiver.pdf")
plot(p2)
dev.off()
```

## Gof: K's method (homo effect)

```{r echo=F}
load("goodness_of_fit_bike/homo_es_Ni.rdata")
load("goodness_of_fit_bike/homo_es_Nj.rdata")
re_i <- c()
for(i in iseq){
  re <- cbind(t(es_Ni_homo_list[[i]]), i)
  colnames(re) <- c("Number of events of senders", "Esimtated cumulative intensity", "Sender")
  re_i <- rbind(re_i, re)
}
re_i %>% as.data.frame() -> re_i
# re_i$Sender %>% as.factor() -> re_i$Sender

re_j <- c()
for(j in iseq){
  re <- cbind(t(es_Nj_homo_list[[j]]), j)
  colnames(re) <- c("Number of events of receivers", "Esimtated cumulative intensity", "Receiver")
  re_j <- rbind(re_j, re)
}
re_j %>% as.data.frame() -> re_j
# re_j$Receiver %>% as.factor() -> re_j$Receiver

```

```{r  echo=F}
ggplot(re_i, aes(x = `Number of events of senders`, y = `Esimtated cumulative intensity`, color = `Sender`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "K's methods: sender",
       x = "Number of events of senders",
       y = "Estimated cumulative intensity") + 
  theme_minimal() -> p1
p1
```
```{r echo=F, eval=F}
pdf(file = "goodness_of_fit_bike/Homo_sender.pdf")
plot(p1)
dev.off()
```
```{r echo=F}
ggplot(re_j, aes(x = `Number of events of receivers`, y = `Esimtated cumulative intensity`, color = `Receiver`)) +
  geom_point(size = 0.5) +
  geom_abline(intercept = 0, slope = 1, color = "black", linetype = "dashed") + 
  labs(title = "K's methods: receiver",
       x = "Number of events of receivers",
       y = "Estimated cumulative intensity") +
  theme_minimal() -> p2
p2
```
```{r echo=F, eval=F}
pdf(file = "goodness_of_fit_bike/Homo_receiver.pdf")
plot(p2)
dev.off()
```


